\mbox{TRITON: Neural Neural Textures for Better Sim2Real}

### 2022-06-18 CORL/example.tex
Submitted Paper

@@

\usepackage{corl_2022} % Use this for the initial submission.
% \usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{multirow}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{array, booktabs, ragged2e}

@@

% \title{TRITON: Globally Consistent Sim-to-Real Transfer
\title{Neural Neural Textures Make Better Simulators

``I Can't Believe It's Not Real!''%Definitely gonna delete this lol
 %via Neural Textures
 }

@@

\begin{abstract}
	% Abstracts should be a single paragraph, between 4--6 sentences long, ideally. Gross violations will trigger corrections at the camera-ready phase.
	% Because of the 6 sentence limit, I've commented out some of the sentences...
	Unpaired image translation algorithms can be used for sim-to-real tasks, but most fail to generate temporally consistent results.
	% Because of this, the details or even identity of a particular object might change as it moves across a scene.
	We present a new approach that combines differential rendering with image translation to achieve temporal consistency over indefinite timescales.
%
	%TURNING TWO SENTENCES INTO ONE:
	% We call this algorithm TRITON (Texture Recovering Image Translation Network): an unsupervised, end-to-end, stateless sim-to-real algorithm.
	% Unlike previous techniques, TRITON leverages the underlying 3d geometry of input scenes by generating realistic-looking learnable neural textures.
	We call this algorithm TRITON (Texture Recovering Image Translation Network): an unsupervised, end-to-end, stateless sim-to-real algorithm that 
	leverages the underlying 3d geometry of input scenes by generating realistic-looking learnable neural textures.
%
	% These textures are projected onto the surfaces of input scenes, which are then fed through an image translation network to obtain the final outputs.
	By settling on a particular albedo for the objects in a scene, we ensure consistency between frames statelessly.
	Unlike previous algorithms, TRITON is not limited to camera movements --- it can handle the movement of objects as well, making it useful for downstream tasks such as robotic manipulation.
	Our experiments show that in addition to achieving higher temporal consistency, the translations are closer to ground truth photographs than previous techniques.
\end{abstract}
\keywords{sim to real, image translation, differentiable rendering}

%===============================================================================
\section{Introduction}
Problem: 
Why is this problem important?
No view consistency.

Introducing our intuition of what improvements can solve this problem.

Our exact method - introducing our components and what we're doing

Conclusion: This works well, and our contributions are x

@@

%===============================================================================
\section{Formulation}
\label{sec:data}
	\begin{figure}[thbp]
	\vspace{-10pt}
		\begin{center}
			\includegraphics[width=\textwidth]{../images/first_diagram.pdf}
		\end{center}
		\vspace{-5pt}
		\caption{
			This is an overview of what TRITON accomplishes.
			TRITON learns the textures of 3d objects to help translate simulated images into photographs. It does this with unpaired data. Each row is a different dataset.
			}
		\label{fig:first_diagram}
	\end{figure}
	% TRITON stands for Texture Recovering Image Translation Network. It has two goals: to translate images, and to recover textures.

	TRITON's goal is to turn 3d simulated images into realistic fake photographs (by training it without any matching pairs), while maintaining high surface consistency.
	It does this by simultaneously learning both an image translator and a set of realistic textures.
	These translations can be useful for downstream tasks, especially robotic policy learning from camera data, enabling sim2real.

	In contrast to previous works involving `neural textures' \textbf{(mryoo: cite them here)}, TRITON can handle more than just camera movements:
	the positions of objects in the training data can be moved around or deformed as well between data samples.
	For this reason, we chose the term ``surface consistency'' instead of ``view consistency'', which was the term used in [] \textbf{(mryoo: cite)}.
	With high surface consistency, surfaces of translated objects will look the same even when moved around or viewed from different camera angles.

	\begin{figure}[H]
		\begin{center}
			\includegraphics[width=400pt]{../images/uvl_explanation_minimal.pdf}
		\end{center}
		\caption{
			A scene is obtained by rendering a 3d state into an image, where the first two color channels represent $u,v$ coordinates and the third channel $l$ represents object labels.
			% This diagram shows the purpose of a UVL image.
			% A UVL scene is an image that has three channels: RGB.
			% R and G are used for U and V, and B is used for L.
			% L stands for Label, and determines which part of the synthetic image will get which texture.
			% The U and V coordinates correspond to positions on each texture,
			% telling it how to project the textures onto the 3d objects represented in the UVL scene.
			% The darkest shade of blue corresponds to the 1st texture, and the next darkest shade of blue corresponds to the 2nd texture etc.
			}
		\label{fig:uvl_explanation}
	\end{figure}

	There are two components to every dataset: A set of simulated 3d scenes, and a set of photographs.
	Datasets usually have many more scenes than photographs, since scenes can be generated automatically.

	% The photographs, having $(r,g,b)$ values between 0 and 1,
	% 	are denoted as $p \in [0,1]^{N \times 3 \times H \times W}$ where $N$ is the batch size,
	% 	3 refers to the three $(r,g,b)$ channels, 
	% 	and $H,W$ are the height and width respectively.

	% A photograph in a set of photographs, having $(r,g,b)$ values between 0 and 1,
	% 	is denoted as ${p^n \in [0,1]^{ 3 \times H \times W}}$ where $n$ is that photograph's index in that set,
	% 	3 refers to the three $(r,g,b)$ channels, 
	% 	and $H,W$ are the height and width respectively.

	A photograph is an image tensor, having $(r,g,b)$ values between 0 and 1,
		is denoted as ${p \in [0,1]^{ 3 \times H \times W}}$ where 
		3 refers to the three $(r,g,b)$ channels, 
		and $H,W$ are the height and width respectively.

	In this work, a scene refers to a rendered 3d simulation state - which includes the position, rotation, and deformation of every object (including the camera).
	% Using some 3d rendering software, be it Blender or Gazebo or some other 3d creates an image from these 
	We represent each 3d state with a simple $(r,g,b)$ image, in a simple enough format that any decent simulator should able to provide.
	% These have the same datatype and dimensions as photographs and are denoted as 
	% $s \in [0,1]^{N \times 3 \times H \times W}$.
	% A scene has the same dimensions as a photograph and is denoted as 
	% $s^n \in [0,1]^{3 \times H \times W}$.
	A scene has the same dimensions as a photograph and is denoted as 
	$s \in [0,1]^{3 \times H \times W}$.
	However, unlike $p$, $s$'s three $(r,g,b)$ channels encode a special semantic meaning: $(u,v,l)$ as depicted in figure \ref{fig:uvl_explanation}.
	The channels $u$ and $v$ refer to a texture coordinate, whereas $l$ refers to a label value that identifies every object in a scene.
	In a given dataset, each object gets a different label. Likewise, each object is assigned a different texture.
	We assume that every dataset has $L$ different label values, $L$ different objects, and that we must learn $L$ different neural textures.

TODO: Say I scales and discretizes l, don't say more than that. 
% 	In each dataset, we must also define a function $I(l)$ that maps label values to texture indices. A simple way to do this is with the following definition:
% 	\begin{equation}
% 		I: \left\{\frac{1}{L},\frac{2}{L},\dots \frac{L}{L}\right\} \rightarrow \left\{1,2,\dots L\right\}  \eqand  I(l)=l\cdot L
% 	\end{equation}
	However, this mapping can be changed arbitrarily if its more convenient to do so for a given dataset.
	Also please note that this paper uses 1-based indexing for notational simplicity.

@@

% %===============================================================================
\section{Method} \label{sec:method}
	\begin{figure}[thbp]
	    \vspace{-20pt}
		\begin{center}
			% \includegraphics[width=400pt]{../images/main_diagram_condensed.pdf}
			% \includegraphics[width=400pt]{../images/main_diagram_condensed_with_domains.pdf}
			\includegraphics[width=\textwidth]{../images/main_diagram_beautiful.pdf}
		\end{center}
		\vspace{-10pt}
		\caption{
			% We use differentiable rendering paired with unpaired image translation to consistently= transform synthetic scenes into realistic images.
			% To ensure all objects look consistent in different positions and views, we learn the albedo of each object's surface by using a learnable latent texture.
			% This texture is parametrized as an image generated by an MLP which is fed Fourier features, as shown in figure \ref{fig:learnable_textures}.
			% $N$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
			%
			%JUNE 12:
			%Don't say 4 main components; say 2 components and 2 losses
			%TODO: Try to use right-angled arrows
			%TODO: Use tau as a function
			%Copy paste the figure multiple times, deleting things
			%Mention "Neural Neural Texture": Its a function mapping UV to RGB
			%Formulation doesnt mentino texture; just uvl inputs and final outputs
			%Always use function notation tauuv instead of just tau (in figure as well) 
			%The arrow should be running through tau. It's not a variable its a function...
			%Rename 'B' to "N" for batch size
			%Figure 8: Align consistent with inconsistent and use all 5 green ones
			%
			This figure is an overview TRITON.
			Inputs are on the left, and outputs are on the right.
			The dashed arrows indicate losses.
			Although $\pi\toN$ and $\ph\toN$ look similar, they are not identical - $\lTR$ encourages them to look as similar as possible.
			% $\pi$ is simply projected textures, whereas $\hat{p}$ has been run through an image translator, allowing it to have shadows and specularities.
			% TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
			% TODO: Use variables instead of 3,4
			% TODO: Make the text larger and easier to read
			% TODO: Simplify the diagram?
		}
		\label{fig:main_diagram}
	\end{figure}

		In this section, we describe how TRITON works to translate images from domain A (simulation) to domain B (photos) while maintaining surface consistency. 
		TRITON has four main components: a neural texture, an image translator, and two surface consistency losses. [[One or two sentences summarizing the flow - nothing more than that]].

		%JUNE 12:
		%TODO: MIgrate all four of these teasers into their respective subsections to save space.

	\subsection{Neural Neural Texture Projection}
		\begin{figure}[thbp]
		    \vspace{-15pt}
			\begin{center}
				\includegraphics[width=300pt]{../images/learnable_textures.pdf}
			\end{center}
			\vspace{-3pt}
			\caption{
				This figure illustrates how the our neural neural textures are calculated in figure \ref{fig:main_diagram}. They are fully differentiable, and represented continuously along the texture's U and V axes using Fourier feature networks.
			}
			\vspace{-10pt}
			% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
			% We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
			% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
			\label{fig:learnable_textures}
		\end{figure}

@@

		% Using neural neural textures, we can encode features directly onto the surfaces of the 3d objects in a scene, which the image translation module uses to maintain visual consistency between states and viewpoints.
		Instead of feeding a scene $s$ directly into the image translator $\Tab$, we first apply learnable textures $\psi$ to its surfaces as shown in figure \ref{fig:main_diagram}.
		Previous works called these learnable textures ``neural textures'', and were parametrized by a discrete grid of differentiable texels. 
		% In contrast, we call our learnable textures ``neural nerual textures'', becuase our textures are a type of neural texture that is parametrized continuously over UV space using a neural fourier feature network.
		In contrast, we call our learnable textures ``neural nerual textures'', becuase our textures are parametrized continuously over UV space using a neural network.
		Like previous works, our neural textures $\psi\toL$ are learned jointly with our image translator $T$.

		These neural neural textures are represented implicitly by a neural network that maps UV values to RGB values. %, and are used to obtain projections $\pi$ from 3d scenes $s$.
		For each texture $\psi^i \in \psi\toL$, 
		\begin{equation}
			\psi^i: (u,v) \in\real^2 \rightarrow (r,g,b) \in\real^3 % \eqand 
		\end{equation}

		Given a scene $s$, we obtain projection $\pi$ by applying a texture $\psi^i \in \psi\toL$ to every pixel $(u,v,l) \in s$ individually, where texture index $i=I(l)$ is decided by the label value $l$ of that scene pixel.
		% Each pixel in the resulting projection $rgb\in\pi$ is the result of selecting a texture index $i$ based on the rank of label value $l$, then applying $\psi^i$ to the $u,v$ values.
		\begin{equation}
			% \pi=\psi\toL(s) \eqand rgb \in \pi = \psi^i(uv)
			% \pi_{n,c,x,y}=\psi^i(s_{n,1,x,y},s_{n,2,x,y}) \eqwhere 1\le n\le N,\ \  1\le c\le 3 ,\ \ 1\le x\le W,\ \ 1\le y\le H,\ \ \text{and} \ \ i=I(s_{n,3,x,y})
			% \pi_{n,c,x,y}=\psi^i(s_{n,1,x,y},s_{n,2,x,y})
			\pi_{[x,y]}=\psi^i(s_{[x,y,1]},s_{[x,y,2]})
		\end{equation}
		% where $1\le n\le N,\ \ 1\le c\le 3 ,\ \ 1\le x\le W,\ \ 1\le y\le H,\ \ \text{and} \ \ i=I(s_{n,3,x,y})$.
		% where $n\in \{1\dots N\},\ \ c\in \{1\dots 3\} ,\ x\in \{1\dots W\},\ y\in \{1\dots H\},\ \ \text{and} \ \ i=I(s_{n,3,x,y})$.
		where $ x\in \{1\dots W\},\ y\in \{1\dots H\}$, and texture index $i=I(l)$ where $l=s_{[x,y,3]}$ and subscript means multidimensional indexing.

@@

	\subsection{Image Translation}
	\label{sec:image_translation}

	% 	\begin{figure}[H]
	% 		\begin{center}
	% 			\includegraphics[width=200pt]{../images/module_translator.pdf}
	% 		\end{center}
	% 		\caption{
	% 			A subset of figure \ref{fig:main_diagram} focusing on the image translation module $T$.
	% 		}
	% 		% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
	% 		% We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
	% 		% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
	% 		\label{fig:module_translator}
	% 	\end{figure}

@@

\section{Experiments}\label{sec:results}

\subsection{Datasets}
Here we detail the datasets used in our experiments. 
Every dataset has two sets of images: UVL scenes and real photographs. They are all unpaired, and have RGB values ranging from 0 to 1.

The first dataset to mention is the three-block dataset.  
It has 300 photos and 2000 UVL scenes. It features a table with three alphabet blocks on a table, which are randomly translated along the X and Y axes and rotated randomly along the Z axis. Each photograph features these three cubes with a random position and rotation.

[[Insert photographs and UVL maps here; a digram showing each dataset we describe here and 1 or two samples of each domain in each dataset]]

@@

>>>>

\addtolength{\floatsep}{-2mm}
\addtolength{\textfloatsep}{-1mm}
\addtolength{\intextsep}{-1mm}
\renewcommand{\baselinestretch}{0.99}

@@

\usepackage{corl_2022} % Use this for the initial submission.
% \usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{multirow}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{array, booktabs, ragged2e}
\usepackage{comment}

@@

% \title{TRITON: Globally Consistent Sim-to-Real Transfer
\title{\mbox{TRITON: Neural Neural Textures for Better Sim2Real}
%``I Can't Believe It's Not Real!''%Definitely gonna delete this lol
%via Neural Textures
}

@@

\begin{abstract}
	%Current sim-to-real image translation algorithms do not generate consistent results across large timeframes when the objects in an environment are allowed to move, making it difficult to train good robotic policies using them.
	%To address this problem, we introduce a new algorithm called TRITON (Texture Recovering Image Translation Network): an unsupervised end-to-end image translation algorithm that combines neural rendering with image translation to maintain temporal consistency over arbitrarily long timeframes.
	%Unlike previous sim-to-real image translation algoithms, TRITON leverages the underlying 3d structure of the simulated images to learn realistic textures on the surfaces of objects.
	%We introduce a new type of nerual texture called a ``neural neural texture'', as well as separate losses each of which are capable of accomplishing this consistency goal.
% 	As far as we are aware, this is the first algorihtm to attempt to learn the albedo of dynamically moving 3d objects without supervision.
	%We demonstrate the supeiority of our approach both qualitatively and quantitatively, using robotic experiments and comparisons to ground truth photographs. We show that TRITON generates more realistic images than other algoithms do.
	Unpaired image translation algorithms can be used for sim2real tasks, but most fail to generate temporally consistent results.
	We present a new approach that combines differentiable rendering with image translation to achieve temporal consistency over indefinite timescales, using surface consistency losses and \emph{neural neural textures}.
	We call this algorithm TRITON (Texture Recovering Image Translation Network): an unsupervised, end-to-end, stateless sim2real algorithm that 
	leverages the underlying 3d geometry of input scenes by generating realistic-looking learnable neural textures.
	By settling on a particular texture for the objects in a scene, we ensure consistency between frames statelessly.
	Unlike previous algorithms, TRITON is not limited to camera movements --- it can handle the movement of objects as well, making it useful for downstream tasks such as robotic manipulation.
% 	Our experiments show that in addition to achieving higher temporal consistency, the translations are closer to ground truth photographs than previous techniques.
		We demonstrate the superiority of our approach both qualitatively and quantitatively, using robotic experiments and comparisons to ground truth photographs. We show that TRITON generates more useful images than other algorithms do.
\end{abstract}
\keywords{sim2real, image translation, differentiable rendering}

%===============================================================================
\section{Introduction}

% INTRODUCE:
%     Image Translation
%         For Videos
%     Differentiable Rendering
%         Neural Textures
%             They combine image translation
%     Most similar to our work is blah

Current sim2real image translation algorithms used for robotics \cite{retina_gan,rl_cyclegan} often have difficulty generating consistent results across large time-frames particularly when the objects in an environment are allowed to move. This makes training good robotic policies using such sim2real challenging.
In this paper, we discuss an algorithm called TRITON (Texture Recovering Image Translation Network) that combines neural rendering, image translation, and two special surface consistency losses to create surface-consistent translations.
We use the term surface-consistent to refer to the desirable quality of preserving the visual appearance of object surfaces as they move, or are viewed from another angles.

TRITON is applicable when we have a simulator capable of generating a realistic distribution of geometric data, but when we do not have any information about the surfaces of those objects (which we need to render realistic images). For example, in our experiments we use a robotic arm model provided by the manufacturer that contains no material information, and then learn to render the materials of the arm using TRITON.
As opposed to requiring an artist to create 3d models with meaningful textures, TRITON can generate these from scratch using a set of photographs capturing the distribution of states in a simulation, without requiring any matches between domains. 
% TRITON is robust to small camera variations, and can recover crisp textures even if the geometry isn't perfect.

We conduct multiple experiments to confirm TRITON's advantage over prior image translation approaches commonly used for sim2real including CycleGAN~\cite{cyclegan} and CUT~\cite{cut}.
%First, we train it on a dataset with alphabet blocks, then compare photographs in that dataset to TRITON outputs by manually aligning the simulated 3d cubes with the photographs.
Important, we show the advantages of the proposed approach in real-robot sim2real experiments, learning the textures and training a robot policy solely based on the images generated by TRITON. 
%We also perform a robotic experiment, where we learn a policy completely in a simulation, and then verify it in the real world. In both of these tests, TRITON outperforms other image translation algorithms.

\begin{figure}[thbp]
	\vspace{-10pt}
		\begin{center}
			\includegraphics[width=\textwidth]{../images/first_diagram.pdf}
		\end{center}
		\vspace{-5pt}
		\caption{
			This is an overview of what TRITON accomplishes.
			TRITON learns the textures of 3d objects to help translate simulated images into photographs. It does this with unpaired data. Each row is a different dataset.
			}
		\label{fig:first_diagram}
	\vspace{-5pt}
	\end{figure}

\vspace{-5pt}	
\section{Related Works}
\vspace{-3pt}
\paragraph{Unsupervised Image to Image and Video to Video Translation}
Generative models have been very successful in creating images unconditionally~\cite{gan,stylegan}, creating images conditioned on text~\cite{dalle,imagen} and creating images when trained on paired data~\cite{pixtopix}.
Generative models that translate images between unpaired data is a challenging task as well, but has been done before~\cite{dual_diffusion,cyclegan,munit,unit}.
Of particular interest are sim2real image to image translation algorithms such as~\cite{retina_gan,rl_cyclegan,surgical_image_translation,enhancing_photorealism_enhancement}. These algorithms aim to translate simulated images into realistic ones, for various purposes such as data augmentation or video game enhancement. In particular, \citet{retina_gan,rl_cyclegan} are used to help train robots. Our paper uses an architecture based on~\citet{surgical_image_translation}, which is based on MUNIT~\cite{munit}.
This area of research has been extended to video to video translation, where optical flow is often used to create a stateful translation where temporal coherence is preserved~\cite{tecogan,mocyclegan}. These algorithms fail to provide temporal coherence over long time periods, however. Another work from~\citet{surgical_video_translation}, is closely related to ours and uses neural rendering to translate videos with temporal coherence even when the camera spins around all the way.

\vspace{-8pt}
\paragraph{View Synthesis}
View synthesis is a field of research where we predict the outputs of unseen camera viewpoints. NeRF \cite{nerf} has spawned a large body of research on end to end view synthesis, resulting in works such as \cite{nerv,fast_nerf,barf}. Related to our work, which also uses geometry based backbone are \cite{free_view_synthesis,stable_view_synthesis,ners}. All of these works, however, only work with static scenes. There are NeRF-based approaches that work on dynamic scenes \cite{dnerf,nerfies,nerualradianceflow} but none of these interactive. \citet{playable_environments} is interactive, but its conditioned on learned actions and not compatible with physics simulators that would be used to train robots.

\vspace{-8pt}
\paragraph{Neural Textures}
\citet{deferred_neural_rendering} introduced the concept of neural textures and image translators in the context of a deferred rendering pipeline, used in other works such as \cite{surgical_video_translation} which is closely related to our project. 
\citet{surgical_video_translation} differs from TRITON in a few very important aspects though, the biggest being that it only synthesizes new camera views, where the only difference between each scene is the placement of the camera. In contrast, our algorithm takes in scenes where several objects are placed in different places or deformed, so that one static  global 3d model of the environment is not sufficient to accomplish our tasks. In addition, TRITON uses a new type of neural texture called a ``neural neural texture'', which is represented continuously using a fourier feature network, as described in \citep{fourier_feature_networks}.

% Problem: 
% Why is this problem important?
% No view consistency.

% Introducing our intuition of what improvements can solve this problem.

% Our exact method - introducing our components and what we're doing

% Conclusion: This works well, and our contributions are x

@@

%===============================================================================
% \vspace{-5pt}
\section{Formulation}
\label{sec:data}
\vspace{-3pt}
	% TRITON stands for Texture Recovering Image Translation Network. It has two goals: to translate images, and to recover textures.
	TRITON's goal is to turn 3d simulated images into realistic fake photographs (by training it without any matching pairs), while maintaining high surface consistency.
	It does this by simultaneously learning both an image translator and a set of realistic textures.
	These translations can be useful for downstream tasks, especially robotic policy learning from camera data, enabling sim2real.

	In contrast to previous works involving ``neural textures'' \cite{deferred_neural_rendering,surgical_video_translation}, TRITON can handle more than just camera movements:
	the positions of objects in the training data can be moved around or deformed as well between data samples.
% 	For this reason, we chose the term ``surface consistency'' instead of ``view consistency'', which was the term used in [] \textbf{(mryoo: cite)}.
	With high surface consistency, surfaces of translated objects will look the same even when moved around or viewed from different camera angles.

	\begin{figure}[H]
	    \vspace{-5pt}
		\begin{center}
			\includegraphics[width=.8\textwidth]{../images/uvl_explanation_minimal.pdf}
		\end{center}
		\vspace{-10pt}
		\caption{
			A scene is obtained by rendering a 3d state into an image, where the first two color channels represent $u,v$ coordinates and the third channel $l$ represents object labels.
			% This diagram shows the purpose of a UVL image.
			% A UVL scene is an image that has three channels: RGB.
			% R and G are used for U and V, and B is used for L.
			% L stands for Label, and determines which part of the synthetic image will get which texture.
			% The U and V coordinates correspond to positions on each texture,
			% telling it how to project the textures onto the 3d objects represented in the UVL scene.
			% The darkest shade of blue corresponds to the 1st texture, and the next darkest shade of blue corresponds to the 2nd texture etc.
			}
		\label{fig:uvl_explanation}
		\vspace{-15pt}
	\end{figure}

	There are two components in every dataset: A set of simulated 3d scenes, and a set of photographs.
	Datasets usually have many more scenes than photographs, since scenes can be generated automatically.
	% The photographs, having $(r,g,b)$ values between 0 and 1,
	% 	are denoted as $p \in [0,1]^{N \times 3 \times H \times W}$ where $N$ is the batch size,
	% 	3 refers to the three $(r,g,b)$ channels, 
	% 	and $H,W$ are the height and width respectively.
	% A photograph in a set of photographs, having $(r,g,b)$ values between 0 and 1,
	% 	is denoted as ${p^n \in [0,1]^{ 3 \times H \times W}}$ where $n$ is that photograph's index in that set,
	% 	3 refers to the three $(r,g,b)$ channels, 
	% 	and $H,W$ are the height and width respectively.
	A photograph is an image tensor, having $(r,g,b)$ values between 0 and 1,
		is denoted as ${p \in [0,1]^{H \times W \times 3}}$ where 
		3 refers to the three $(r,g,b)$ channels, 
		and $H,W$ are the height and width respectively.

	In this work, a scene refers to a rendered 3d simulation state - which includes the position, rotation, and deformation of every object (including the camera).
	% Using some 3d rendering software, be it Blender or Gazebo or some other 3d creates an image from these 
	We represent each 3d state with a simple $(r,g,b)$ image, in a simple enough format that any decent simulator should able to provide.
	% These have the same datatype and dimensions as photographs and are denoted as 
	% $s \in [0,1]^{N \times 3 \times H \times W}$.
	% A scene has the same dimensions as a photograph and is denoted as 
	% $s^n \in [0,1]^{3 \times H \times W}$.
	A scene has the same dimensions as a photograph and is denoted as 
	$s \in [0,1]^{H \times W \times 3}$.
	However, unlike $p$, $s$'s three $(r,g,b)$ channels encode a special semantic meaning: $(u,v,l)$ as depicted in Figure \ref{fig:uvl_explanation}.
	The channels $u$ and $v$ refer to a texture coordinate, whereas $l$ refers to a label value that identifies every object in a scene.
	In a given dataset, each object gets a different label. Likewise, each object is assigned a different texture.
	We assume that every dataset has $L$ different label values, $L$ different objects, and that we must learn $L$ different neural textures.
    % TODO: Say I scales and discretizes l, don't say more than that. 
% 	In each dataset, we must also define a function $I(l)$ that maps label values to texture indices. A simple way to do this is with the following definition:
% 	\begin{equation}
% 		I: \left\{\frac{1}{L},\frac{2}{L},\dots \frac{L}{L}\right\} \rightarrow \left\{1,2,\dots L\right\}  \eqand  I(l)=l\cdot L
% 	\end{equation}
% 	However, this mapping can be changed arbitrarily if its more convenient to do so for a given dataset.
% 	Also please note that this paper uses 1-based indexing for notational simplicity.

@@

% %===============================================================================
\vspace{-8pt}
\section{Method} \label{sec:method}
	\begin{figure}[thbp]
	    \vspace{-15pt}
		\begin{center}
			% \includegraphics[width=400pt]{../images/main_diagram_condensed.pdf}
			% \includegraphics[width=400pt]{../images/main_diagram_condensed_with_domains.pdf}
			\includegraphics[width=0.9\textwidth]{../images/main_diagram_beautiful.pdf}
		\end{center}
		\vspace{-10pt}
		\caption{
			% We use differentiable rendering paired with unpaired image translation to consistently= transform synthetic scenes into realistic images.
			% To ensure all objects look consistent in different positions and views, we learn the albedo of each object's surface by using a learnable latent texture.
			% This texture is parametrized as an image generated by an MLP which is fed Fourier features, as shown in figure \ref{fig:learnable_textures}.
			% $N$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
			%
			%JUNE 12:
			%Don't say 4 main components; say 2 components and 2 losses
			%TODO: Try to use right-angled arrows
			%TODO: Use tau as a function
			%Copy paste the figure multiple times, deleting things
			%Mention "Neural Neural Texture": Its a function mapping UV to RGB
			%Formulation doesnt mentino texture; just uvl inputs and final outputs
			%Always use function notation tauuv instead of just tau (in figure as well) 
			%The arrow should be running through tau. It's not a variable its a function...
			%Rename 'B' to "N" for batch size
			%Figure 8: Align consistent with inconsistent and use all 5 green ones
			%
			This figure is an overview TRITON.
			Inputs are on the left, and outputs are on the right.
			The dashed arrows indicate losses.
			Although $\pi\toN$ and $\ph\toN$ look similar, they are not identical - $\lTR$ encourages them to look as similar as possible.
			% $\pi$ is simply projected textures, whereas $\hat{p}$ has been run through an image translator, allowing it to have shadows and specularities.
			% TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
			% TODO: Use variables instead of 3,4
			% TODO: Make the text larger and easier to read
			% TODO: Simplify the diagram?
		}
		\label{fig:main_diagram}
	\end{figure}
		In this section, we describe how TRITON works to translate images from domain A (simulation) to domain B (photos) while maintaining surface consistency. 
		TRITON introduces a learneable neural neural texture with two novel surface consistency losses to an existing image translator. In the end, TRITON is able to effectively generate photorealistic images.
		%JUNE 12:
		%TODO: MIgrate all four of these teasers into their respective subsections to save space.
\vspace{-3pt}
	\subsection{Neural Neural Texture Projection}
	\vspace{-3pt}
		\begin{figure}[thbp]
		    \vspace{-5pt}
			\begin{center}
				\includegraphics[width=0.6\textwidth]{../images/learnable_textures.pdf}
			\end{center}
			\vspace{-3pt}
			\caption{
				This figure details how our neural neural textures are calculated in Figure~\ref{fig:main_diagram}. They are fully differentiable, and represented continuously along the texture's u and v axes using Fourier feature networks.
			}
			\vspace{-10pt}
			% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
			% We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
			% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
			\label{fig:learnable_textures}
		\end{figure}

@@

		% Using neural neural textures, we can encode features directly onto the surfaces of the 3d objects in a scene, which the image translation module uses to maintain visual consistency between states and viewpoints.
		Instead of feeding a scene $s$ directly into the image translator $\Tab$, we first apply learnable textures $\psi$ to its surfaces as shown in Figure \ref{fig:main_diagram}.
		Previous works called these learnable textures ``neural textures'', and were parametrized by a discrete grid of differentiable texels. 
		% In contrast, we call our learnable textures ``neural nerual textures'', becuase our textures are a type of neural texture that is parametrized continuously over UV space using a neural fourier feature network.
		In contrast, we call our learnable textures as ``neural nerual textures'', because our textures themselves are represented as a neural network function, parameterized continuously over UV space.
		Our neural textures $\psi\toL$ are learned jointly with our image translator $T$.

		These neural neural textures are represented implicitly by a neural network that maps UV values to RGB values. %, and are used to obtain projections $\pi$ from 3d scenes $s$.
		For each texture $\psi^i \in \psi\toL$, 
		\begin{equation}
			\psi^i: (u,v) \in\real^2 \rightarrow (r,g,b) \in\real^3 % \eqand 
		\end{equation}
		Given a scene $s$, we obtain projection $\pi$ by applying a texture $\psi^i \in \psi\toL$ to every pixel $(u,v,l) \in s$ individually, where texture index $i=I(l)$ is decided by the label value $l$ of that scene pixel.
		% Each pixel in the resulting projection $rgb\in\pi$ is the result of selecting a texture index $i$ based on the rank of label value $l$, then applying $\psi^i$ to the $u,v$ values.
		\begin{equation}
			% \pi=\psi\toL(s) \eqand rgb \in \pi = \psi^i(uv)
			% \pi_{n,c,x,y}=\psi^i(s_{n,1,x,y},s_{n,2,x,y}) \eqwhere 1\le n\le N,\ \  1\le c\le 3 ,\ \ 1\le x\le W,\ \ 1\le y\le H,\ \ \text{and} \ \ i=I(s_{n,3,x,y})
			% \pi_{n,c,x,y}=\psi^i(s_{n,1,x,y},s_{n,2,x,y})
			\pi_{[x,y]}=\psi^i(s_{[x,y,1]},s_{[x,y,2]})
		\end{equation}
		% where $1\le n\le N,\ \ 1\le c\le 3 ,\ \ 1\le x\le W,\ \ 1\le y\le H,\ \ \text{and} \ \ i=I(s_{n,3,x,y})$.
		% where $n\in \{1\dots N\},\ \ c\in \{1\dots 3\} ,\ x\in \{1\dots W\},\ y\in \{1\dots H\},\ \ \text{and} \ \ i=I(s_{n,3,x,y})$.
		where $ x\in \{1\dots W\},\ y\in \{1\dots H\}$. Texture index $i = I(l)$ where $l=s_{[x,y,3]}$ and the function $I(\cdot)$ scales and discretizes $l$ into integers. Subscripts mean multidimensional indexing.

@@

\vspace{-3pt}
	\subsection{Image Translation}
	\label{sec:image_translation}
\vspace{-3pt}
	% 	\begin{figure}[H]
	% 		\begin{center}
	% 			\includegraphics[width=200pt]{../images/module_translator.pdf}
	% 		\end{center}
	% 		\caption{
	% 			A subset of figure \ref{fig:main_diagram} focusing on the image translation module $T$.
	% 		}
	% 		% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
	% 		% We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
	% 		% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
	% 		\label{fig:module_translator}
	% 	\end{figure}

@@

	%===============================================================================
\vspace{-8pt}
\section{Experiments}\label{sec:results}
\vspace{-3pt}
\subsection{Datasets}
\vspace{-2pt}
%Here we detail the datasets used in our experiments.
% We constructed multiple datasets for our experiments.
We constructed two datasets AlphabetCube-3 and RobotPose-xArm to benchmark different image translators in many perspectives.
In our setting, each dataset is composed of two sets of unpaired images: UVL scenes from a simulator and real photographs.
Note that the images in all datasets are unpaired and UVL scenes only rely on rough 3d models of the objects in the scene without need of precisely aligning objects in the simulator to the real world.
% . They are all unpaired, and have RGB values ranging from 0 to 1.
We use AlphabetCube-3 for image translation quality evaluation, and RobotPose-xArm for sim2real policy learning evaluation.

% The first dataset we particularly use for the offline evaluation is the three-block dataset.

% [[Insert photographs and UVL maps here; a digram showing each dataset we describe here and 1 or two samples of each domain in each dataset]]

@@

\end{comment}
